\documentclass[11pt]{article}
\usepackage[margin=0.82in]{geometry}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{array}
\usepackage{float}
\newcolumntype{L}[1]{>{\raggedright\arraybackslash}p{#1}}

\title{Project Three: Statistical Integrity Tests for Fund X}
\author{Prepared by Harman Singh for Professor Phelim Boyle}
\date{June 2026}

\begin{document}
\maketitle

\section*{Data Box}
The analysis uses 113 monthly observations from January 2017 through May 2026. Returns are measured in percent per month.

\begin{table}[H]
\centering
\caption{Summary Statistics Used Across Tests}
\begin{tabular}{lrr}
\toprule
Statistic & Fund X & S\&P 500 TR \\
\midrule
Sample mean (\%) & 3.50 & 1.33 \\
Sample standard deviation (\%) & 4.01 & 4.54 \\
Positive months & 108 & 80 \\
Negative months & 5 & 33 \\
Monthly Sharpe ratio & 0.87 & 0.29 \\
\bottomrule
\end{tabular}
\end{table}

\section*{Test 1: Wald-Wolfowitz Runs Test}
Fund X has 11 observed sign runs, with 108 positive months and 5 negative months.
The expected number of runs under independent signs is 10.56, with variance 0.73.
The maximum possible number of runs is $R_{max}=2n_-+1=11$, and Fund X reaches that maximum.

For the smoothing alternative, the relevant one-sided concern is too few runs.
The exact lower-tail probability $P(R\leq 11)$ is 1.000.
The normal approximation gives $Z=0.52$ and a two-sided p-value of 0.605.
The test does not flag Fund X. More importantly, the test has little discriminatory power here because only five months are negative; once those five losses are isolated, the run count cannot rise further.

\section*{Test 2: Bollen-Pool Discontinuity Test}
Assuming normal returns with Fund X's mean and standard deviation, the probability of a negative month is 0.192.
This implies 21.66 expected negative months, compared with 5 observed negative months.
The binomial lower-tail p-value is 4.64e-06.
The S\&P 500 benchmark has $p_-=0.385$, 43.51 expected negative months, 33 observed negative months, and p-value 0.025.

Fund X's near-zero count is 5 months in $(0\%,0.5\%)$ and 3 months in $(-0.5\%,0\%)$, for a near-zero ratio of 1.67.
The five negative months are 2017-06 (-0.35\%); 2017-08 (-1.26\%); 2022-06 (-0.32\%); 2022-09 (-0.21\%); 2024-05 (-2.20\%).
The normality and independence assumptions both make the formal p-value too severe for Fund X: positive skewness reduces the true left-tail probability, and positive serial correlation lowers the effective sample size.

\section*{Test 3: Serial Autocorrelation Test}
The first three raw autocorrelations for Fund X are $\rho_1=0.347$, $\rho_2=0.157$, and $\rho_3=0.222$.
The first-order t-statistic is 3.90, with p-value 0.0002.
The S\&P 500 first-order autocorrelation is -0.138.

The active return series, Fund X minus S\&P 500 TR, has autocorrelations $\rho_1=0.013$, $\rho_2=-0.026$, and $\rho_3=0.080$.
Its first-order t-statistic is 0.14, with p-value 0.891.
The Ljung-Box p-value through 12 lags is 0.0001 for raw Fund X returns and 0.857 for active returns.

This pattern supports level-persistence rather than return smoothing. The raw Fund X returns are serially correlated, but the active returns are not.
The naive annualised Sharpe ratio is 3.02.
Using Lo's 12-lag adjustment gives 1.76; using 6 lags gives 2.05.
Both adjusted values remain economically exceptional.

\section*{Test 4: Abdulali Bias Ratio}
Using Fund X's sample standard deviation of 4.01\%, the upper interval $[0,\hat\sigma]$ contains 80 returns and the lower interval $[-\hat\sigma,0)$ contains 5 returns.
The observed bias ratio is therefore 13.33.
Under a normal distribution with Fund X's monthly Sharpe ratio, the expected bias ratio is approximately 2.11, already above Abdulali's usual warning thresholds for low-Sharpe hedge funds.

The bootstrap calibration uses 100,000 resamples of the 113 observed Fund X returns.
The bootstrap median is 13.17, the mean is 15.23, and the 90\% interval is [7.30, 28.67].
The observed bias ratio is at the 51.9th percentile of the bootstrap distribution.
The S\&P 500 bias ratio is 2.85.
The high Fund X bias ratio is typical for its own return distribution and reflects genuine high positive-return frequency, not a small-positive bunching anomaly.

\clearpage
\section*{Overall Assessment}
\begin{table}[H]
\centering
\caption{Summary of Statistical Integrity Tests}
\begin{tabular}{L{0.19\linewidth}L{0.24\linewidth}L{0.25\linewidth}L{0.21\linewidth}}
\toprule
Test & Key statistic & Assessment & Caveat \\
\midrule
Runs test & $R=11$, $R_{max}=11$ & No evidence of too few runs & Few negative months limits test power \\
Bollen-Pool & $n_-=5$ vs expected 21.66; p=4.64e-06 & Formal test is extreme & Normality and independence assumptions overstate significance \\
Serial autocorrelation & Raw $\rho_1=0.347$; active $\rho_1=0.013$ & Supports level-persistence, not smoothing & Raw returns alone are misleading \\
Bias ratio & BR=13.33; bootstrap percentile 51.9 & Typical for Fund X's own distribution & Abdulali thresholds are not calibrated to high-Sharpe funds \\
\bottomrule
\end{tabular}
\end{table}

Taken together, the tests do not provide statistical evidence of return smoothing or mechanical avoidance of losses.
They cannot rule out every possible concern about Fund X, but they do not support the specific irregularities these tests were designed to detect.

\end{document}
