\documentclass[11pt]{article}
\usepackage[margin=0.85in]{geometry}
\usepackage{booktabs}
\usepackage{array}
\usepackage{longtable}
\usepackage{float}
\usepackage{hyperref}

\title{Project 1A LSQ Fund Update}
\author{Prepared for Professor Phelim Boyle}
\date{June 2026}

\begin{document}
\maketitle

\section*{Data \& Method}
The update uses 113 monthly LSQ observations from January 2017 through May 2026.
The original paper used 109 observations ending in January 2026; the added LSQ returns are Feb 2026 = 1.88\%, Mar 2026 = 3.68\%, Apr 2026 = 2.95\%, May 2026 = 7.64\%.
The LSQ analysis uses the baseline net-of-fees return series from the Spartan monthly performance PDF.

For the benchmark, I used the Yahoo Finance \texttt{\string^SP500TR} S\&P 500 Total Return Index.
This is the appropriate S\&P 500 series because the paper states that the benchmark returns are calculated with dividends reinvested; a price-only S\&P 500 index would omit dividends and understate the benchmark return.

For 2026-05, the market comparators are pulled from Yahoo Finance monthly adjusted levels. The S\&P 500 TR return is 5.263305\%, and the NVIDIA return is 5.797466\%.

All return inputs are monthly.
Population standard deviation divides by $N$.
Sharpe ratios use a 0\% risk-free rate.
Sortino ratios use the paper's downside-deviation convention.
Omega is computed as $\sum \max(r_t-L,0) / \sum \max(L-r_t,0)$.
Alpha and beta are estimated from the monthly regression of LSQ returns on S\&P 500 Total Return Index returns.

\clearpage
\section*{Updated Table 2}
\setcounter{table}{1}
\input{tables/updated_table_2.tex}

\clearpage
\section*{Updated Table 4}
\setcounter{table}{3}
\input{tables/updated_table_4.tex}

\clearpage
\section*{Summary of Changes}
\subsection*{Table 2: Paper Values vs Updated Values}
\small
\begin{center}
\begin{tabular}{lrrr}
\toprule
Metric & Paper & Updated & Change \\
\midrule
LSQ arithmetic monthly return & 3.48\% & 3.50\% & +0.02 pp \\
LSQ geometric monthly return & 3.40\% & 3.42\% & +0.02 pp \\
LSQ percent positive months & 95.40\% & 95.58\% & +0.18 pp \\
LSQ percent negative months & 4.60\% & 4.42\% & -0.18 pp \\
LSQ population standard deviation & 4.06\% & 3.99\% & -0.07 pp \\
LSQ Sharpe ratio & 0.86 & 0.88 & +0.02 \\
LSQ Sortino ratio & 13.96 & 14.36 & +0.40 \\
LSQ Omega ratio & 88.28 & 92.00 & +3.72 \\
Alpha, monthly & 3.52\% & 3.53\% & +0.01 pp \\
Beta & -0.04 & -0.02 & +0.02 \\
\bottomrule
\end{tabular}
\end{center}
\normalsize

\subsection*{Table 4: Paper LSQ Column vs Updated LSQ Column}
\small
\begin{center}
\begin{tabular}{lrrr}
\toprule
Statistic & Paper LSQ & Updated LSQ & Change \\
\midrule
Arithmetic Mean Return & 3.47 & 3.50 & +0.03 \\
Geometric Mean Return & 3.40 & 3.42 & +0.02 \\
Percent Positive Months & 95.41 & 95.58 & +0.17 \\
Percent Negative Months & 4.59 & 4.42 & -0.17 \\
Average Positive Month & 3.68 & 3.70 & +0.02 \\
Average Negative Month & -0.87 & -0.87 & +0.00 \\
Standard Deviation & 4.06 & 3.99 & -0.07 \\
Sharpe Ratio & 0.86 & 0.88 & +0.02 \\
Sortino Ratio & 13.96 & 14.36 & +0.40 \\
Omega Ratio & 88.28 & 92.00 & +3.72 \\
\bottomrule
\end{tabular}
\end{center}
\normalsize

\subsection*{Interpretation}
The updated LSQ statistics move only moderately because 4 months are being added to a 109-month sample.
All added LSQ months are positive, so the number of positive months rises from 104 to 108 and the number of negative months remains five.
The average monthly return rises relative to the paper because May 2026 is a strong positive month.
The maximum drawdown remains -2.20\% because none of the added months creates a new trough.

The risk-adjusted metrics remain very strong.
The Sharpe ratio is 0.88, the Sortino ratio is 14.36, and the zero-threshold Omega ratio is 92.00.
The updated monthly alpha is 3.53\% and beta is -0.02, so the evidence still supports the paper's conclusion that LSQ's returns are not explained by broad equity-market exposure.

\clearpage
\section*{Additional Analysis: Serial Correlation}
Since the paper already identifies serial correlation as an important feature of the LSQ return series, I implemented a serial-correlation diagnostic table and a Newey-West adjusted inference table.
Newey-West inference adjusts the standard errors for autocorrelation and heteroskedasticity in the regression residuals.
This gives a more appropriate t-statistic when monthly returns are not independent over time.

\subsection*{Serial-Correlation Diagnostics}
\begin{table}[H]
\centering
\caption{Serial-Correlation Diagnostics for Monthly Returns}
\label{tab:serial-correlation}
\small
\begin{tabular}{lrrrr}
\toprule
Series & $\rho_1$ & LB p(1) & LB p(6) & LB p(12) \\
\midrule
LSQ Fund & 0.35 & 0.0002 & 0.0001 & 0.0001 \\
S\&P 500 TR & -0.14 & 0.1370 & 0.5007 & 0.3521 \\
LSQ minus S\&P 500 TR & 0.01 & 0.8885 & 0.9880 & 0.8567 \\
\bottomrule
\end{tabular}

\vspace{0.15cm}
\begin{minipage}{0.86\linewidth}
\footnotesize
$\rho_1$ is the first-order monthly autocorrelation.
LB p($k$) is the Ljung-Box p-value through lag $k$.
\end{minipage}
\end{table}

\subsection*{Newey-West Adjusted Inference}
\begin{table}[H]
\centering
\caption{Conventional vs Newey-West Inference}
\label{tab:newey-west}
\small
\begin{tabular}{lrrrrr}
\toprule
Statistic & Estimate & OLS SE & OLS t-stat & Newey-West SE & Newey-West t-stat \\
\midrule
LSQ monthly mean & 3.50\% & 0.38\% & 9.27 & 0.53\% & 6.57 \\
Monthly alpha & 3.53\% & 0.39\% & 8.93 & 0.59\% & 5.98 \\
Beta & -0.02 & 0.08 & -0.27 & 0.11 & -0.21 \\
\bottomrule
\end{tabular}

\vspace{0.15cm}
\begin{minipage}{0.92\linewidth}
\footnotesize
Newey-West standard errors use 4 monthly lags, based on the rule $\lfloor 4(T/100)^{2/9}\rfloor$ with $T=113$.
The alpha-beta regression is $r_{\mathrm{LSQ},t}=\alpha+\beta r_{\mathrm{S\&P500TR},t}+\varepsilon_t$.
\end{minipage}
\end{table}

The Newey-West adjustment increases the standard errors, which is expected when there is positive serial correlation.
Even after this adjustment, the LSQ monthly mean and alpha remain economically large and statistically strong.
The beta remains close to zero and statistically insignificant.

\subsection*{Additional Suggestions}
I think the most logical next extension would be to apply the same dependence-aware approach to the paper's nonlinear performance ratios.
We could produce confidence intervals for the Sharpe, Sortino, and Omega ratios without assuming independent monthly observations.
This should directly address the serial-correlation issue and preserve our focus on asymmetric performance.

\end{document}
